PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected difference score chunks base-prepan

# Difference score for prepandemic and baseline phq sum scores
dat.glad <- dat.glad %>%
  mutate(
    phq.diff_score_prepan_base =
      as.numeric(
        phq.sum_score_prepan - phq.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

@@

# Difference score for prepandemic and baseline gad sum scores
dat.glad <- dat.glad %>%
  mutate(
    gad.diff_score_prepan_base =
      as.numeric(
        gad.sum_score_prepan - gad.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

@@

PCL difference scores
NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
```{r pcl difference scores}
# Difference score for prepandemic and baseline pcl sum scores
dat.glad <- dat.glad %>%
  mutate(
    pcl.diff_score_prepan_base =
      as.numeric(
        pcl.sum_score_prepan - pcl.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

>>>>

# Difference score for prepandemic and baseline phq sum scores
dat.glad <- dat.glad %>%
  mutate(
    phq.diff_score_prepan_base =
      as.numeric(
        phq.sum_score_base - phq.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

@@

# Difference score for prepandemic and baseline gad sum scores
dat.glad <- dat.glad %>%
  mutate(
    gad.diff_score_prepan_base =
      as.numeric(
        gad.sum_score_base - gad.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )

@@

PCL difference scores
NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
```{r pcl difference scores}
# Difference score for prepandemic and baseline pcl sum scores
dat.glad <- dat.glad %>%
  mutate(
    pcl.diff_score_prepan_base =
      as.numeric(
        pcl.sum_score_base - pcl.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
      )
  )
